Estimating Neighborhood Rents with Scraped Data

### 2018-06-03 dashboard/index.rmd
update to main index, also settled navbar for now

---
output: 
  flexdashboard::flex_dashboard:
    navbar:
       - {title: "hesscl.com", href: "http://hesscl.com", align: right}
       - {title: "Project Home", icon: "fa-home", href: "http://hesscl.com/smooth-sea/index.html", align: right} 
    orientation: columns
    theme: bootstrap
    logo: "../logo.svg"
    source_code: "https://github.com/hesscl/smooth-sea"
---

>>>>

---
title: "smooth-sea"
output: 
  flexdashboard::flex_dashboard:
    navbar:
       - {title: "hesscl.com", href: "http://hesscl.com", align: right}
       - {title: "Project Home", href: "http://hesscl.com/smooth-sea/index.html", align: left} 
    orientation: columns
    theme: bootstrap
    logo: "../logo.svg"
---

### 2018-06-03 index.rmd
update to main index, also settled navbar for now

@@

[`flexdashboard` for working paper's model diagnostics and forecasts](./dashboard/index.html)

[GitHub Repository](https://github.com/hesscl/smooth-sea/)

>>>>

### Objective

The goal of this research is to understand the spatial and temporal dynamics of rent estimates in Seattle using scraped rental housing listings from Craigslist. I use a series of data visualizations to describe the overall datam, after which I model a panel of quarterly census tract estimates to explain the dynamics observed so far and forecast a surface of rent values for the current quarter.

@@

[`flexdashboard`](./dashboard/index.html) for working paper's model diagnostics and forecasts

[GitHub Repository](https://github.com/hesscl/smooth-sea/) with source code for manuscript and results dashboard
